Computation and comparison of the stable Northeastern US marine boundary layer

### 2020-12-02 Paper/main.tex
Update paper sections

\author{
  Shreyas Ananthan\footnote{SOME JOB TITLE, AIAA Member},
  Michael J. Brazell\footnote{Researcher III, High-Performance Algorithms and Complex Fluids, AIAA Member},
  Ganesh Vijayakumar\footnote{Researcher III, Mechanical Engineering, AIAA Member}, and
}
\affil{National Renewable Energy Laboratory, Golden CO 80401}

@@

{\renewcommand\arraystretch{1.0}
\noindent\begin{longtable*}{@{}l @{\quad=\quad} l@{}}
$\alpha$  & Wind shear exponent  \\
$f$       & Frequency \\
$L$       & Turbulent integral length scale \\
$u_\tau$   & Friction velocity    \\
$R_{ij}$   & Two point correlation tensor \\
$TI$      & Turbulence intensity \\
$TKE$     & Turbulent kinetic energy 
\end{longtable*}}

\section{Introduction}
\fxnote{Update this introduction.}

@@

\subsection{Study objective and outline}

The current paper is organized as follows.

@@

\section*{Appendix}

An Appendix, if needed, should appear before the acknowledgments.

>>>>

\author{
  Shreyas Ananthan\footnote{Researcher V, High-Performance Algorithms and Complex Fluids, AIAA Member},
  Michael J. Brazell\footnote{Researcher III, High-Performance Algorithms and Complex Fluids, AIAA Member},
  Ganesh Vijayakumar\footnote{Researcher III, Mechanical Engineering, AIAA Member}, and
}
\affil{National Renewable Energy Laboratory, Golden CO 80401}

@@

{\renewcommand\arraystretch{1.0}
\noindent\begin{longtable*}{@{}l @{\quad=\quad} l@{}}
$\alpha$  & Wind shear exponent  \\
$f$       & Frequency \\
$f_{max}$  & Maximum resolvable frequency due to mesh limits \\
$f_{Ny}$   & Nyquist frequency \\
$L$       & Turbulent integral length scale \\
$u_\tau$   & Friction velocity    \\
$R_{ij}$   & Two point correlation tensor \\
$TI$      & Turbulence intensity \\
$TKE$     & Turbulent kinetic energy 
\end{longtable*}}

\section{Introduction}
%\fxnote{Update this introduction.}

@@

\subsection{Objectives}
In the current study on stable marine boundary layers, we aim to build
on the previous work in the literature and complete several
objectives.  First, a series of stable boundary layer conditions will
be computed using the Exawind solvers which match the measurements of
Archer et al \cite{archer2016predominance}.  The behavior of the
stable boundary layers, including mean flow quantities and turbulent
statistics, are examined and compared to the neutral and unstable
cases computed in \cite{cheung2020large}.  Secondly, we examine the
domain and mesh requirements necessary to capture the turbulent scales
for the stable offshore boundary layers.  Finally, two LES solvers
within the Exawind project are compared in this study: the
unstructured, incompressible Navier-Stokes solver Nalu-Wind and the
structured, adaptive mesh refinement solver AMR-Wind.  Both codes are
used to calculate the same stable boundary layer, and the relative
differences between the codes are reported.

@@

%% \section*{Appendix}

%% An Appendix, if needed, should appear before the acknowledgments.

### 2020-12-02 Paper/results.tex
Update paper sections

%%%%%%%%%%% Grid resolution spectra figure %%%%%%%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/GridStudy/GridStudy_Spectra.ipynb
\begin{figure}%[hbt!]
  \centering
  \fxnote{remove AMR-Wind results from graphs}\\
  \includegraphics[width=2.0in]{figures/GridStudy_Spectra_Su.png}
  \includegraphics[width=2.0in]{figures/GridStudy_Spectra_Sv.png}
  \includegraphics[width=2.0in]{figures/GridStudy_Spectra_Sw.png}
  \caption{   \label{fig:GridStudySpectra} 
    Calculation of the wind spectra $S_i$ for LES of stable
    5m/s case with different resolutions.  The gray vertical lines
    correspond to the maximum resolvable frequency $f_{max}$ according
    to equation (\ref{eq:fmax}). }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%% Grid resolution Rij correlation figure %%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/GridStudy/GridStudy_Rij.ipynb
\begin{figure}%[hbt!]
  \centering
  \fxnote{remove AMR-Wind results from graphs}\\
  \includegraphics[width=2.5in]{figures/GridStudy_Rij_Longitudinal.png}
  \includegraphics[width=2.5in]{figures/GridStudy_Rij_Lateral.png}
  \caption{\label{fig:GridStudyRij} Calculation of the averaged
    longitudinal and lateral $\langle R_{11}(\boldsymbol{\xi})
    \rangle$ coefficient at $z$=20m for LES of stable 5m/s case with
    different resolutions.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Similar conclusions can be drawn by examining the turbulent integral
length scale $L$.  This lengthscale can be calculated from $\langle
R_{11}(\boldsymbol{\xi}) \rangle$ via
\begin{equation}
  L = \int_0^\infty \langle R_{11}(\xi) \rangle \: {\textrm d}\xi
\end{equation}
and the results are shown in table \ref{tab:GridStudyLscale}.  With a
resolution of 2.5m, the ratio of the longitudinal length scale to the
grid size $L/\textrm{d}x \approx 10.1$, while in the lateral direction
$L/\textrm{d}x \approx 2.36$, suggesting even finer resolution is
required to capture the lateral scales.

@@

%%%%%%%%%%% z=20m snapshot pics %%%%%%%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
\begin{figure}[hbt!]
  \centering
  \fxnote{label plots using pstricks: 5m/s on top, 15m/s on bottom} \\
  \includegraphics[width=3.0in]{figures/snapshots/05ms/velh_mag_z20.png}
  \includegraphics[width=3.0in]{figures/snapshots/05ms/velz_z20.png} \\

  \includegraphics[width=3.0in]{figures/snapshots/10ms/velh_mag_z20.png}
  \includegraphics[width=3.0in]{figures/snapshots/10ms/velz_z20.png} \\

  \includegraphics[width=3.0in]{figures/snapshots/15ms/velh_mag_z20.png}
  \includegraphics[width=3.0in]{figures/snapshots/15ms/velz_z20.png} \\
  \caption{ \label{fig:SnapshotsZ20} Snapshots of the horizontal
    velocity and vertical velocity, taken at t=20,000 seconds of the
    simulations at height z=20m.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%% Grid resolution spectra figure %%%%%%%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/GridStudy/GridStudy_Spectra.ipynb
\begin{figure}%[hbt!]
  \centering
  \includegraphics[width=2.0in]{figures/GridStudy_Spectra_Su.png}
  \includegraphics[width=2.0in]{figures/GridStudy_Spectra_Sv.png}
  \includegraphics[width=2.0in]{figures/GridStudy_Spectra_Sw.png}
  \caption{   \label{fig:GridStudySpectra} 
    Calculation of the wind spectra $S_i$ for LES of stable
    5m/s case with different resolutions.  The gray vertical lines
    correspond to the maximum resolvable frequency $f_{max}$ according
    to equation (\ref{eq:fmax}). }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%% Grid resolution Rij correlation figure %%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/GridStudy/GridStudy_Rij.ipynb
\begin{figure}%[hbt!]
  \centering
  \includegraphics[width=2.5in]{figures/GridStudy_Rij_Longitudinal.png}
  \includegraphics[width=2.5in]{figures/GridStudy_Rij_Lateral.png}
  \caption{\label{fig:GridStudyRij} Calculation of the averaged
    longitudinal and lateral $\langle R_{11}(\boldsymbol{\xi})
    \rangle$ coefficient at $z$=20m for LES of stable 5m/s case with
    different resolutions.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Additional information about the mesh and domain requirements can be
drawn by examining the turbulent integral length scale $L$.  This
lengthscale can be calculated from $\langle R_{11}(\boldsymbol{\xi})
\rangle$ via
\begin{equation}
  L = \int_0^\infty \langle R_{11}(\xi) \rangle \: {\textrm d}\xi
\end{equation}
and the results are shown in table \ref{tab:GridStudyLscale}.  With a
resolution of 2.5m, the ratio of the longitudinal length scale to the
grid size $L/\textrm{d}x \approx 10.1$, while in the lateral direction
$L/\textrm{d}x \approx 2.36$, suggesting even finer resolution is
required to capture the lateral scales.

@@

%%%%%%%%%%% z=20m snapshot pics %%%%%%%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
\begin{figure}[hbt!]
  \centering
  \fxnote{label plots using pstricks: 5m/s on top, 15m/s on bottom} \\
  \includegraphics[width=3.0in]{figures/snapshots/05ms/velh_mag_z20.png}
  \includegraphics[width=3.0in]{figures/snapshots/05ms/velz_z20_samelimits.png} \\

  \includegraphics[width=3.0in]{figures/snapshots/10ms/velh_mag_z20.png}
  \includegraphics[width=3.0in]{figures/snapshots/10ms/velz_z20_samelimits.png} \\

  \includegraphics[width=3.0in]{figures/snapshots/15ms/velh_mag_z20.png}
  \includegraphics[width=3.0in]{figures/snapshots/15ms/velz_z20_samelimits.png} \\
  \caption{ \label{fig:SnapshotsZ20} Snapshots of the horizontal
    velocity and vertical velocity, taken at t=20,000 seconds of the
    simulations at height z=20m.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
